The responses of \textit{Spinifex littoreus} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2020-12-06 tex/interactcsesample.tex
rectify the Introduction section

\begin{keywords}
Sections; lists; figures; tables; mathematics; fonts; references; appendices
\end{keywords}

@@

In order to assist authors in the process of preparing a manuscript for a journal, the Taylor \& Francis `\textsf{Interact}' layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ bibliography style file and a sample bibliography are also provided in order to assist with the formatting of your references.

Commands that differ from or are provided in addition to standard \LaTeXe\ are described in this document, which is \emph{not} a substitute for a \LaTeXe\ tutorial.

The \texttt{interactcsesample.tex} file can be used as a template for a manuscript by cutting, pasting, inserting and deleting text as appropriate, using the preamble and the \LaTeX\ environments provided (e.g.\ \verb"\begin{abstract}", \verb"\begin{keywords}").

\subsection{The \textsf{Interact} class file}\label{class}

The \texttt{interact} class file preserves the standard \LaTeXe\ interface such that any document that can be produced using \texttt{article.cls} can also be produced with minimal alteration using the \texttt{interact} class file as described in this document.

If your article is accepted for publication it will be typeset as the journal requires in Minion Pro and/or Myriad Pro. Since most authors will not have these fonts installed, the page make-up is liable to alter slightly with the change of font. Also, the \texttt{interact} class file produces only single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter if necessary during preparation of the proofs. Please therefore do not try to match the typeset format exactly, but use the standard \LaTeX\ fonts instead and ignore details such as slightly long lines of text or figures/tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of manuscripts prepared using \emph{\LaTeX}}

Manuscripts for possible publication should be submitted to the Editors for review as directed in the journal's Instructions for Authors, and in accordance with any technical instructions provided in the journal's ScholarOne Manuscripts or Editorial Manager site. Your \LaTeX\ source file(s), the class file and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

Please ensure that any author-defined macros used in your article are gathered together in the preamble of your .tex file, i.e.\ before the \verb"\begin{document}" command. Note that if serious problems are encountered in the coding of a document (missing author-defined macros, for example), the typesetter may resort to rekeying it.

\section{Using the \texttt{interact} class file}

For convenience, simply copy the \texttt{interact.cls} file into the same directory as your manuscript files (you do not need to install it in your \TeX\ distribution). In order to use the \texttt{interact} document class, replace the command \verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{interact}".

The following document-class options should \emph{not} be used with the \texttt{interact} class file:
\begin{itemize}
  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
  \item \texttt{oneside}, \texttt{twoside} -- not necessary, \texttt{oneside} is the default;
  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
  \item \texttt{twocolumn} -- should not be used (see Subsection~\ref{class});
  \item \texttt{onecolumn} -- not necessary as it is the default style.
\end{itemize}
To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default. The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.

%If your manuscript has supplementary content you can use the \verb"interact" class file to prepare all or part of it using the \verb"suppldata" document-class option, which will suppress the `article history' date. This option \emph{must not} be used on any primary content. Note that authors are solely responsible for the preparation of all supplemental material.

\section{Additional features of the \texttt{interact} class file}

\subsection{Title, authors' names and affiliations, abstracts and article types}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for double-blind peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to hide the author name(s) and affiliation(s) temporarily.
Next you should include the abstract if your article has one, enclosed within an \texttt{abstract} environment.
The \verb"\articletype" command is also provided as an \emph{optional} element which should \emph{only} be included if your article actually needs it.
For example, the titles for this document begin as follows:
\begin{verbatim}
\articletype{ARTICLE TEMPLATE}

\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact}
layout + Council of Science Editors name-year reference style)}

\author{
\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author.
Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany} }

\begin{abstract}
This template is for authors who are preparing a manuscript for a
Taylor \& Francis journal using the \LaTeX\ document preparation system
and the \texttt{interact} class file, which is available via selected
journals' home pages on the Taylor \& Francis website.
\end{abstract}
\end{verbatim}

An additional abstract in another language (preceded by a translation of the article title) may be included within the \verb"abstract" environment if required.

A graphical abstract may also be included if required. Within the \verb"abstract" environment you can include the code
\begin{verbatim}
\\\resizebox{25pc}{!}{\includegraphics{abstract.eps}}
\end{verbatim}
where the graphical abstract is to appear, where \verb"abstract.eps" is the name of the file containing the graphic (note that \verb"25pc" is the recommended maximum width, expressed in pica, for the graphical abstract in your manuscript).

\subsection{Abbreviations}

A list of abbreviations may be included if required, enclosed within an \texttt{abbreviations} environment, i.e.\ \verb"\begin{abbreviations}"\ldots\verb"\end{abbreviations}", immediately following the \verb"abstract" environment.

\subsection{Keywords}

A list of keywords may be included if required, enclosed within a \texttt{keywords} environment, i.e.\ \verb"\begin{keywords}"\ldots\verb"\end{keywords}". Additional keywords in other languages (preceded by a translation of the word `keywords') may also be included within the \verb"keywords" environment if required.

\subsection{Subject classification codes}

AMS, JEL or PACS classification codes may be included if required. The \texttt{interact} class file provides an \texttt{amscode} environment, i.e.\ \verb"\begin{amscode}"\ldots\verb"\end{amscode}", a \texttt{jelcode} environment, i.e.\ \verb"\begin{jelcode}"\ldots\verb"\end{jelcode}", and a \texttt{pacscode} environment, i.e.\ \verb"\begin{pacscode}"\ldots\verb"\end{pacscode}" to assist with this.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" command may be used to create additional footnotes to the title or authors' names if required. Footnote symbols for this purpose should be used in the order
$^\ast$~(coded as \verb"$^\ast$"), $\dagger$~(\verb"$\dagger$"), $\ddagger$~(\verb"$\ddagger$"), $\S$~(\verb"$\S$"), $\P$~(\verb"$\P$"), $\|$~(\verb"$\|$"),
$\dagger\dagger$~(\verb"$\dagger\dagger$"), $\ddagger\ddagger$~(\verb"$\ddagger\ddagger$"), $\S\S$~(\verb"$\S\S$"), $\P\P$~(\verb"$\P\P$").

Note that any \verb"footnote"s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package may be used to set the notes at the end of your text, before the bibliography. The symbols will be changed to match the style of the journal if necessary by the typesetter.}

@@

\subsection{Sections}

The \textsf{Interact} layout style allows for five levels of section heading, all of which are provided in the \texttt{interact} class file using the standard \LaTeX\ commands \verb"\section", \verb"\subsection", \verb"\subsubsection", \verb"\paragraph" and \verb"\subparagraph". Numbering will be automatically generated for all these headings by default.

\subsection{Lists}

Numbered lists are produced using the \texttt{enumerate} environment, which will number each list item with arabic numerals by default. For example,
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g.\ \verb"\item[(i)] first item"\, to create a list numbered with roman numerals at level one.

Bulleted lists are produced using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\subsection{Figures}

The \texttt{interact} class file will deal with positioning your figures in the same way as standard \LaTeX. It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{figure} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate figures from the text.

Figure captions appear below the figures themselves, therefore the \verb"\caption" command should appear after the body of the figure. For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
\begin{verbatim}
\begin{figure}
\centering
\subfloat[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
\subfloat[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}
\end{verbatim}
\begin{figure}
\centering
\subfloat[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
\subfloat[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}

To ensure that figures are correctly numbered automatically, the \verb"\label" command should be included just after the \verb"\caption" command, or in its argument.

The \verb"\subfloat" command requires \verb"subfig.sty", which is called in the preamble of the \texttt{interactcsesample.tex} file (to allow your choice of an alternative package if preferred) and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Please supply any additional figure macros used with your article in the preamble of your .tex file.

The source files of any figures will be required when the final, revised version of a manuscript is submitted. Authors should ensure that these are suitable (in terms of lettering size, etc.) for the reductions they envisage.

The \texttt{epstopdf} package can be used to incorporate encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc. Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

@@

\subsection{Landscape pages}

If a figure or table is too wide to fit the page it will need to be rotated, along with its caption, through 90$^{\circ}$ anticlockwise. Landscape figures and tables can be produced using the \verb"rotating" package, which is called by the \texttt{interact} class file. The following commands (for example) can be used to produce such pages.
\begin{verbatim}
\setcounter{figure}{1}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}
\begin{verbatim}
\setcounter{table}{1}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption (the value of the counter being the number given to the preceding figure or table). Subsequent captions will then be automatically renumbered accordingly. The \verb"\epsfbox" command requires \verb"epsfig.sty", which is called by the \texttt{interact} class file and is also included in the \textsf{Interact} \LaTeX\ bundle for convenience.

Please note that if the \verb"endfloat" package is used, one or both of the commands
\begin{verbatim}
\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\DeclareDelayedFloatFlavor{sidewaystable}{table}
\end{verbatim}
will need to be included in the preamble of your .tex file, after the \verb"endfloat" package is loaded, in order to process any landscape figures and/or tables correctly.

\subsection{Theorem-like structures}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \texttt{interact} class file), as follows:
\begin{proof}
More recent algorithms for solving the semidefinite programming relaxation are particularly efficient, because they explore the structure of the MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, definition, remark, etc.) need to be defined as required, e.g.\ using \verb"\newtheorem{theorem}{Theorem}" in the preamble of your .tex file (see the preamble of \verb"interactcsesample.tex" for more examples). You can define the numbering scheme for these structures however suits your article best. Please note that the format of the text in these environments may be changed if necessary to match the style of individual journals by the typesetter during preparation of the proofs.

\subsection{Mathematics}

\subsubsection{Displayed mathematics}

The \texttt{interact} class file will set displayed mathematical formulas centred on the page without equation numbers if you use the \texttt{displaymath} environment or the equivalent \verb"\[...\]" construction. For example, the equation
\[
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\]
was typeset using the commands
\begin{verbatim}
\[
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text for future reference, use the \texttt{equation} environment, e.g.
\begin{equation}
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
     \label{subeqnparta}
\end{equation}
\begin{equation}
     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
     \label{subeqnpartb}
\end{equation}
\end{subequations}
which was typeset using the commands
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
     \label{subeqnparta}
\end{equation}
\begin{equation}
     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{amsmath} package, which is called by the class file. If you put a \verb"\label" just after the \verb"\begin{subequations}" command, references can be made to the collection of equations, i.e.\ `(\ref{subeqnexample})' in the example above. Or, as the example also shows, you can label and refer to each equation individually -- i.e.\ `(\ref{subeqnparta})' and `(\ref{subeqnpartb})'.

Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.

\subsubsection{Math fonts}

\paragraph{Superscripts and subscripts}
Superscripts and subscripts will automatically come out in the correct size in a math environment (i.e.\ enclosed within \verb"\(...\)" or \verb"$...$" commands in running text, or within \verb"\[...\]" or the \texttt{equation} environment for displayed equations). Sub/superscripts that are physical variables should be italic, whereas those that are labels should be roman (e.g.\ $C_p$, $T_\mathrm{eff}$). If the subscripts or superscripts need to be other than italic, they must be coded individually.

\paragraph{Upright Greek characters and the upright partial derivative sign}
Upright lowercase Greek characters can be obtained by inserting the letter `u' in the control code for the character, e.g.\ \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the unit microns -- $\umu\mathrm{m}$) and $\upi$ (the ratio of the circumference of a circle to its diameter). Similarly, the control code for the upright partial derivative $\upartial$ is \verb"\upartial". Bold lowercase as well as uppercase Greek characters can be obtained by \verb"{\bm \gamma}", for example, which gives ${\bm \gamma}$, and \verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

@@

\subsection{References cited in the text}

References should be cited in Council of Science Editors (CSE) name-year style, e.g.\ `\citep{Rit74,Fel81,Fau02}', or `\ldots see \citet[p.~15]{Smi91}'. When several in-text references occur at the same point, distinguish works by the same author published in different years by placing the years after the author name in chronological sequence, e.g.\ `\citep{Smi70,Smi75}'. For two or more works published by the same author in the same year, add an alphabetic designator to the year in both the in-text reference and the end reference, e.g.\ `(\citealp{And60CJPS}, \citeyear{And60CJB})'. When the authors of two works published in the same year have identical surnames, include their initials in the in-text reference and separate the two in-text references by a semicolon and a space, e.g.\ `\citep{DawJ86,DawM86}'. If a work has two authors, give both names in the in-text reference, e.g.\ `\citep{Wei74}'. If a reference has three or more authors, give only the first author's name followed by `et~al.' and the year of publication, e.g.\ `\citep{Och03}'. If the first author's names and the years of publication are identical for several references, include enough co-author names to eliminate ambiguity, e.g.\ `(Martinez, Fuentes, et~al. 1990; Martinez, Fuentes, Ortiz, et~al. 1990)'. For further details on this reference style, see the Instructions for Authors on the Taylor \& Francis website.

Each bibliographic entry has a key, which is assigned by the author and is used to refer to that entry in the text. In this document, the key \verb"Ant97" in the citation form \verb"\citep{Ant97}" produces `\citep{Ant97}', and the keys \verb"{Sha78,AG98,BGC04}" in the citation form \verb"\citep{Sha78,AG98,BGC04}" produce `\citep{Sha78,AG98,BGC04}'. The appropriate citation style for different situations can be obtained, for example, by \verb"\citet{IOM75}" for `\citet{IOM75}', \verb"\citealt{SRW05}" for `\citealt{SRW05}', or \verb"\citealp{Lee03}" for `\citealp{Lee03}'. Citation of the year alone may be produced by \verb"\citeyear{Ste64}", i.e.\ `\citeyear{Ste64}', or \verb"\citeyearpar{Ovi95}", i.e.\ `\citeyearpar{Ovi95}', or of the author(s) alone by \verb"\citeauthor{Wei03}", i.e.\ `\citeauthor{Wei03}'. Optional notes may be included at the beginning and/or end of a citation by the use of square brackets, e.g.\ \verb"\citep[see][p.~73-–77]{PI51}" produces `\citep[see][p.~73--77]{PI51}'; \verb"\citep[e.g.][]{Sch02}" produces `\citep[e.g.][]{Sch02}'. A `plain' \verb"\cite" command will produce the same results as a \verb"\citet", i.e.\ \verb"\cite{Ant03}" will produce `\cite{Ant03}'.

\subsection{The list of references}

References should be listed at the end of the main text in alphabetical order by author, then chronologically.
If there is no identifiable author, use e.g. `\citep{Hbk00}'.
The year of publication is required for all reference types; for newspaper articles and patents, provide the full date of publication including the month and day of the month.
If a date of publication is impossible to find, use `\citeyear{LedND}' in its place. The following list shows some sample references prepared in the Taylor \& Francis CSE name-year style.

\begin{thebibliography}{}

\bibitem[Ambudkar and Gottesman(1998)]{AG98}
Ambudkar~SV, Gottesman~MM, editors. 1998. ABC transporters: biomedical,
  cellular, and molecular aspects. San Diego (CA): Academic Press. (Methods
  in enzymology; vol. 292).

\bibitem[Andrews(1960a)]{And60CJPS}
Andrews~JE. 1960a. Cold hardiness of sprouting wheat as affected by duration of
  hardening and hardening temperature. Can J Plant Sci. 40(1):93--102.

\bibitem[Andrews(1960b)]{And60CJB}
Andrews~JE. 1960b. Cold hardening and cold hardiness of young winter rye
  seedlings as affected by stage of development and temperature. Can J Bot.
  38(3):353--363.

\bibitem[Antani et~al.(2003)]{Ant03}
Antani~S, Long~LR, Thoma~GR, Lee~DJ. 2003. Anatomical shape representation in
  spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
  3rd IASTED International Conference on Visualization, Imaging and
  Image Processing; Sep 8--10; Benalmadena, Spain.

\bibitem[Antonioli(1997)]{Ant97}
Antonioli~GE, editor. 1997. Pacemaker leads 1997. Proceedings of the 3rd
  International Symposium on Pacemaker Leads; Sep 11--13; Ferrara, Italy.
  Bologna: Monducci Editore.

\bibitem[Berrino et~al.(2004)]{BGC04}
Berrino~F, Gatta~G, Crosignani~P. 2004. [Case-control evaluation of screening
  efficacy]. Epidemiol Prev. 28:354--359. Italian.

\bibitem[Dawson~J(1986)]{DawJ86}
Dawson~J. 1986. Animal experiments: conference report. BMJ.
  292(6536):1654--1655.

\bibitem[Dawson~M(1986)]{DawM86}
Dawson~M. 1986. Some examples of necessary continuation and
  possible discontinuation of animal experiments. Acta Physiol Scand Suppl.
  554:194--197.

\bibitem[Fauci(2002)]{Fau02}
Fauci~AS. 2002. Smallpox vaccination policy -- the need for dialogue. N Engl J
  Med. 346(17):1319--1320.

\bibitem[Feller(1981)]{Fel81}
Feller~BA. 1981. Health characteristics of persons with chronic activity
  limitation, United States, 1979. Hyattsville (MD): National Center for
  Health Statistics (US). Report No.: VHS-SER-10/137. Available from: NTIS,
  Springfield, VA; PB88-228622.

\bibitem[Handbook\ldots(2000)]{Hbk00}
Handbook of geriatric drug therapy. 2000. Springhouse (PA): Springhouse.

\bibitem[IOM(1975)]{IOM75}
[IOM] Institute of Medicine (US). 1975. Legalized abortion and the public health:
  report of a study by a committee of the Institute of Medicine. Washington
  (DC): National Academy of Sciences.

\bibitem[Lederer({[date unknown]})]{LedND}
Lederer~J. {[date unknown]}. Alimentation et cancer [Diet and cancer].
  Brussels: Nauwelaerts.

\bibitem[Lee et~al.(2003)]{Lee03}
Lee~DJ, Bates~D, Dromey~C, Xu~X, Antani~S. 2003. An imaging system correlating
  lip shapes with tongue contact patterns for speech pathology research. In:
  Krol~M, Mitra~S, Lee~DJ, editors. CMBS 2003. Proceedings of the 16th IEEE
  Symposium on Computer-Based Medical Systems; 2003 Jun 26--27; New York. Los
  Alamitos (CA): IEEE Computer Society. p.~307--313.

\bibitem[Ochi et~al.(2003)]{Och03}
Ochi~K, Sugiura~N, Komatsuzaki~Y, Nishino~H, Ohashi~T. 2003. Patency of
  inferior meatal antrostomy. Auris Nasus Larynx. 30 Suppl:S57--S60.

\bibitem[Oviedo(1995)]{Ovi95}
Oviedo~S. 1995. Adolescent pregnancy: voices heard in the everyday lives of
  pregnant teenagers [master's thesis]. Denton (TX): University of North Texas.

\bibitem[Piaget and Inhelder(1951)]{PI51}
Piaget~J, Inhelder~B. 1951. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
  [The origin of the idea of chance in the child]. Paris: Presses
  Universitaires de France.

\bibitem[Ritzmann(1974)]{Rit74}
Ritzmann~RE. 1974. The snapping mechanism of \textit{Alpheid} shrimp
  [dissertation]. Charlottesville (VA): University of Virginia.

\bibitem[Savage et~al.(2005)]{SRW05}
Savage~E, Ramsay~M, White~J, Beard~S, Lawson~H, Hunjan~R, Brown~D. 2005. Mumps
  outbreaks across England and Wales in 2004: observational study. BMJ.
  [cited~2005 May 31]; 330(7500):1119--1120. Available from:
  http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119

\bibitem[Schott and Priest(2002)]{Sch02}
Schott~J, Priest~J. 2002. Leading antenatal classes: A practical guide. 2nd ed.
  Boston (MA): Books for Midwives.

\bibitem[Shakelford(1978)]{Sha78}
Shakelford~RT. 1978. Surgery of the alimentary tract. Philadelphia (PA): W.B.
  Saunders; Chapter 2, Esophagoscopy, p.~29--40.

\bibitem[Smith(1970)]{Smi70}
Smith~CE. 1970. Studies on arbovirus epidemiology associated with established
  and developing rice culture. Introduction. Trans R Soc Trop Med Hyg.
  64(4):481--482.

\bibitem[Smith(1975)]{Smi75}
Smith~CE. 1975. The significance of mosquito longevity and blood-feeding
  behaviour in the dynamics of arbovirus infections. Med Biol. 53(5):288--294.

\bibitem[Smith(1991)]{Smi91}
Smith~KL. 1991. New dangers in our field [editorial]. Am J Nucl Eng.
  13(1):15--16.

\bibitem[Stearns(1864)]{Ste64}
Stearns~AA. 1864. Armory {S}quare {H}ospital nursing diary. 70 leaves. Located
  at: History of Medicine Division, National Library of Medicine, Bethesda, MD;
  MS B 372.

\bibitem[Weinstein and Swartz(1974)]{Wei74}
Weinstein~L, Swartz~MN. 1974. Pathologic properties of invading organisms. In:
  Sodeman~WA, editor. Pathologic physiology: Mechanisms of disease. 5th ed.
  Philadelphia (PA): Saunders; p. 135--140.

\bibitem[Weiss(2003 Apr~11)]{Wei03}
Weiss~R. 2003 Apr 11. Study shows problems in cloning people: researchers find
  replicating primates will be harder than other mammals. Washington Post (Home
  Ed.). Sect.~A:12 (col.~1).

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\begin{verbatim}
\begin{thebibliography}{}

\bibitem[Ambudkar and Gottesman(1998)]{AG98}
Ambudkar~SV, Gottesman~MM, editors. 1998. ABC transporters: biomedical,
 cellular, and molecular aspects. San Diego (CA): Academic Press.
 (Methods in enzymology; vol. 292).

\bibitem[Andrews(1960a)]{And60CJPS}
Andrews~JE. 1960a. Cold hardiness of sprouting wheat as affected by
 duration of hardening and hardening temperature. Can J Plant Sci.
 40(1):93--102.

\bibitem[Andrews(1960b)]{And60CJB}
Andrews~JE. 1960b. Cold hardening and cold hardiness of young winter
 rye seedlings as affected by stage of development and temperature.
 Can J Bot. 38(3):353--363.

\bibitem[Antani et~al.(2003)]{Ant03}
Antani~S, Long~LR, Thoma~GR, Lee~DJ. 2003. Anatomical shape
 representation in spine x-ray images. Paper presented at: VIIP 2003.
 Proceedings of the 3rd IASTED International Conference on
 Visualization, Imaging and Image Processing; Sep 8--10; Benalmadena,
 Spain.

\bibitem[Antonioli(1997)]{Ant97}
Antonioli~GE, editor. 1997. Pacemaker leads 1997. Proceedings of the
 3rd International Symposium on Pacemaker Leads; Sep 11--13; Ferrara,
 Italy. Bologna: Monducci Editore.

>>>>

\begin{keywords}
Psammophytes; sand burial; \textit{Spinifex littoreus}; responses, plant osmotic stress
\end{keywords}

@@

\label{Introduction-1}
% 主要介绍沙生植物对海岸生态系统对重要意义
Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, and play an important role in the sustainable development in those regions with rising sea levels, surface subsidence and coastal hazards (Martínez et al. 2004, De Battisti \& Griffin 2020). Recently, due to the influence of both climate change and anthropogenic activities, many coastal sand dunes have been modified or destroyed, and this can, or has potentially led to the retreat of coastlines, disappearance of habitats, loss of biodiversity, and severe degradation of ecosystem functions in coastal sand dunes (Feagin et al. 2005, Schlacher et al. 2011, Qu et al. 2017). With the rapid development of economy in China, most of the coastal sand dunes were also eradicated due to real estate and infrastructure development and tourism activities. Almost no well-preserved coastal sand dunes are left, which apart from the loss of ecological functions and habitats, may ultimately result in coastal erosion and the loss of life, property and economy (Yang et al. 2017). Hard engineering structures have been proved to be costly and detrimental for the protection of coastal regions, so it is very important to select natural and environmentally friendly methods for both the protection and restoration of the remaining coastal dune systems (Hanley et al. 2014).

\label{Introduction-2}
% 主要介绍沙埋与沙生植物对关系
Psammophytes can build and stabilize coastal dunes, which will favor the restoration of their ecological functions due to their specific adaptive strategies (Yuan et al. 1993, Nolet et al. 2018, De Battisti \& Griffin 2020). However, only a few species can survive in these ecosystems due to the harsh environmental stress, such as drought, salt spray, strong winds, and especially the frequent and intensive sand burial (Maun \& Lapierre 1986, Hesp 1991, Maun 1994, Maun 1996, Zhao et al. 2014, Du \& Hesp 2020). Sand burial is commonly considered as the selective force for coastal plant regeneration and survival (Moreno-Casasola 1986, Maun 1996, Hwang et al. 2016, Wang et al. 2019), which can decrease and even eliminate the psammophytes if the sand burial levels are over their tolerance capacity, ultimately giving rise to the alteration of species composition in coastal dune systems (Maun \& Perumal 1999, Miller 2015).

\label{Introduction-3}
% 这一段主要讲海岸沙生植物耐沙埋能力的用处
The tolerance capacity to different sand burial levels is varied among species, which finally affect the initial and subsequent coastal dune development and morphology (Hesp 1989). Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial (Zhou et al. 2015a, Harris et al. 2017, Brown \& Zinnert 2018, Wang et al. 2019), while intensive sand burial will decrease its survival and per plant biomass (Maun 1996, Franks \& Peterson 2003). Wang et al. (2012) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while all decreased with moderate treatments contrasted with the control. In addition, Zhou et al. (2015b) showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial. Elongation of stolons, upward growth of ramets, and development of new adventitious roots are the main adaptive strategies for plants to sand burial, potentially leading to an alteration in the biomass allocation of psammophytes in coastal sand dunes (Dech \& Maun 2006, Frosini et al. 2012, Mendoza-González et al. 2014, Luo et al. 2018).

\label{Introduction-4}
% 这一段主要介绍老鼠乐与研究去意义
Spinifex littoreus, a herbaceous plant, is the dominant species in coastal foredunes in South China. It often grows vigorously above the backshore, and in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins S. hirsutus and S. sericeus (Hesp 1989, 2002). Its peak growth occurs in summer, with two growth forms, including elongation of horizontal stolons and upward growth of vertical ramets, which sprout out from the same vegetative reproduction, and usually can be recognized as the same ramets (Jackson et al. 1986). The leaf apex of S. littoreus is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region (Yang et al. 2017). Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on S. littoreus, particularly its stolons on nebkhas forming the foredune zone (Yang et al. 2017) (Figure 1). However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the frequent sand burial is less studied. Furthermore, local government has planted an invasive species Casuarinas equisetifolia for the stabilization of nebkhas originally formed by S.littoreus, which causes severe damage to this species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure 2). Therefore, understanding the adaptive strategies of S. littoreus to sand burial levels, and its role in the stabilization of coastal dunes are very crucial for the effective coastal management and conservation in South China.

\begin{figure}
  \centering
  \subfloat[\textit{S. littoreus} under natural sand burial.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.jpg}}}\hspace{5pt}
  \subfloat[\textit{C. equisetifolia} danmaged by sand burial.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
  \caption{(a) Intensive sand burial on the Spinifex littoreus nebkhas on Pingtan island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015. (b)The nebkhas formed by Spinifex littoreus was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.} 
  \label{sample-pic}
\end{figure}

\label{Introduction-5}
% 我们的研究假设和研究思路
% 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
In this study, we assume that the different sand burial changes the growth process of S. littoreus, which is the key factor for the plants to adapt to the intense sand burial. Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of S. littoreus under different sand burial levels were simulated and measured in a field experiment, in a growing season on Pingtan Island, Fujian Province, South China.

\section{Material and Methods}
\subsection{Study area}
% 如果手稿要给期刊A4打印了，用 document-class 提供的 largeformat 参数（由 interact.cls）提供
% To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default. The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.

\subsection{Methods}

\section{Results}

\subsection{Influence of sand burial on the height of vertical ramets}

\subsection{Influence of sand burial on the length of horizontal stolons}

\subsection{Influence of sand burial on the biomass allocation}

@@

@@

@@

test\citep{quEffectsSandBurial2017}

\bibliographystyle{tfcse.bst}
\bibliography{interactcsesample}
